Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Finishing
Comments

	We claim that expanding ground sets in this way can continue as long as at least $\ell$ isolated nodes exist.
	Fix the configuration just before the creation of a ground set with $x_i$ for some $i$.
	We show that if at least $\ell$ isolated nodes exist (including $x_i$), then there exists a~perfect partition of ground sets after expanding a ground set with $x_i$.
	To show this claim, we consider a configuration, where the largest ground set of each cluster originates from it (excluding the ground set $\{x_0, y_0\}$).
	In this configuration, each cluster contains:  at most one ground set larger than $1$, possibly some isolated nodes, and possibly the ground set $\{x_0, y_0\}$.
	If $I(x_i)$ contains an isolated node, then we simply obtain a~perfect partition by swapping it with $x_i$.
	In the following, we assume that no isolated nodes exist on $I(x_i)$.
	The largest ground set of $I(x_i)$ is at most $k-1$, because $x_i$ is on $S$.
	Therefore $\{x_0, y_0\}$ is present on $I(x_i)$, and we must evict it to make space for $x_i$.
	To find the cluster for $\{x_0, y_0\}$, observe that we have at most $\ell-1$ clusters with isolated nodes, and we have at least $\ell$ isolated nodes --- hence a~cluster with two isolated nodes exists.
	To find a feasible partition, we swap $\{x_0, y_0\}$ with these two collocated isolated nodes, and then we swap an isolated node from $I(x_i)$ with $x_i$.

@@

\maciek{Suggestion: instead of "this means", I saw exclusively the use of "therefore", "hence" and "thus", and maybe "this implies" in papers}

>>>>

	We claim that expanding ground sets in this way can continue as long as at least $\ell$ isolated nodes exist.
	Fix the configuration just before the creation of a ground set with $x_i$ for some~$i$.
	We show that if at least $\ell$ isolated nodes exist (including $x_i$), then there exists a~perfect partition of ground sets after expanding a ground set with $x_i$.
	To show this claim, we consider a configuration, where the largest ground set of each cluster originates from it (excluding the ground set $\{x_0, y_0\}$).
	In this configuration, each cluster contains:  at most one ground set larger than $1$, possibly some isolated nodes, and possibly the ground set $\{x_0, y_0\}$.
	If $I(x_i)$ contains an isolated node, then we simply obtain a~perfect partition by swapping it with $x_i$.
	In the following, we assume that no isolated nodes exist on $I(x_i)$.
	The largest ground set of $I(x_i)$ is at most $k-1$, because $x_i$ is on $S$.
	Therefore $\{x_0, y_0\}$ is present on $I(x_i)$, and we must evict it to make space for $x_i$.
	To find the cluster for $\{x_0, y_0\}$, observe that we have at most $\ell-1$ clusters with isolated nodes, and we have at least $\ell$ isolated nodes --- hence a~cluster with two isolated nodes exists.
	To find a feasible partition, we swap $\{x_0, y_0\}$ with these two collocated isolated nodes, and then we swap an isolated node from $I(x_i)$ with~$x_i$.

@@

\maciek{(strong) Suggestion: instead of "this means", "meaning", I saw exclusively the use of "therefore", "hence" and "thus", and maybe "this implies" in papers. Also in PPl}
